О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Give the exact value if points in intersection of crosses
Rephrase the definition of \rho-curve

\begin{lemma}
	\label{lem:intervals_cross}
	If \textbf{open} line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains not more than 4 points.
\end{lemma}

@@

\begin{definition}
	A $\rho(k,M_1 M_2)$-curve, where $-|M_1 M_2| < k < |M_1 M_2|$ and $k$ is integer, is the set of points $N$,
	such that for given points $M_1$ and $M_2$
	the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, a $\rho(k,M_1 M_2)$-curve is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.

>>>>

\begin{lemma}
	\label{lem:intervals_cross}
	If \textbf{open} line segments $M_1 M_2$ and $M_3 M_4$ do not intersect,
	%$M_1 \neq M_2$, $M_3 \neq M_4$,
	then the set $cr(M_1,M_2) \cap cr(M_3,M_4)$ is either a straight line or contains 2 or 4 points.
\end{lemma}

@@

\begin{definition}
	For given line segment $M_1 M_2$ and an integer $k$, $-|M_1 M_2| < k < |M_1 M_2|$,
	we define a $\rho(k,M_1 M_2)$-curve as the set of points $N$
	such that the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, a $\rho(k,M_1 M_2)$-curve is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.
